---
format: 
  pdf:
    include-in-header: |
      \usepackage{stix}
geometry: 
  - top=4cm
  - bottom=4cm
  - left=4cm
  - right=4cm
---
```{r}
#| label: setup
#| include: false
library(qrcode)
```

\thispagestyle{empty}

::::{layout="[0.3, 0.4, 0.3]"}
:::{#qrcode-1-1}
\raggedright
```{r}
#| echo: false
qr_code(
  "https://t.me/rbrasiloficial", 
  ecl = "H"
) |> 
  plot()
```
:::
:::{#filer-1-2}
\qquad
:::
:::{#qrcode-1-3}
\raggedleft
```{r}
#| echo: false
qr_code(
  "https://t.me/rbrasiloficial", 
  ecl = "H"
) |> 
  plot()
```
:::
::::
::::{layout="[0.3, 0.4, 0.3]"}
:::{#filler2-1}
\qquad
:::
:::{#texto-2-2}
\centering
\vspace*{\fill}
\fontsize{60}{60}\selectfont
\hphantom{.5em} 
R 
\par
\vspace*{\fill}
\fontsize{30}{34}\selectfont
Brasil 
\par
\vspace*{\fill}
\fontsize{24}{30}\selectfont
no \texttt{telegram} 
\par
\vspace*{\fill}
\fontsize{12}{24}\selectfont
\texttt{https://t.me/rbrasiloficial\quad} 
\par
\vspace*{\fill}
:::
:::{#filler-2-3}
\qquad
:::
::::
:::: {layout="[0.3, 0.63, 0.07]"}
::: {#qrcode-3-1}
\raggedright
```{r}
#| label: qrcode-repo-github
#| fig-align: right
#| echo: false

qr_code(
  "https://github.com/mvf-each-usp/estampa-camiseta-r-brasil",
  ecl = "L"
) |> 
  plot()
```
:::
::: {#texto-3-2}
\raggedleft
\fontsize{6}{8}\selectfont
Feito com:\par
\bullet RStudio, \par
\bullet Quarto, \par
\bullet \LaTeX\ e \par
\bullet amor `S2`
\par
Fonte da estampa $\linefeed$ 
\par
`https://github.com/mvf-each-usp/estampa-camiseta-r-brasil`
\par
Entre e forke à vontade\ \ `=D`
:::
:::{#filler-3-3}
:::
::::
