---
format: pdf
geometry: 
  - top=4cm
  - bottom=4cm
  - left=4cm
  - right=4cm
---
```{r}
#| label: setup
#| include: false
library(qrcode)
```

\thispagestyle{empty}

::::{layout="[0.3, 0.4, 0.3]"}
:::{#col1}
\raggedright
```{r}
#| label: qrcode-R-1
#| echo: false
qr_code(
  "https://t.me/rbrasiloficial", 
  ecl = "H"
) |> 
  plot()
```
:::
:::{#col2}
\centering
\fontsize{80}{80}\selectfont
R
:::
:::{#col3}
\raggedleft
```{r}
#| label: qrcode-R-2
#| echo: false
qr_code(
  "https://t.me/rbrasiloficial", 
  ecl = "H"
) |> 
  plot()
```
:::
::::

\centering

\fontsize{40}{35}\selectfont
Brasil

\fontsize{32}{40}\selectfont
no \texttt{telegram}

\fontsize{16}{30}\selectfont
\texttt{https://t.me/rbrasiloficial}


\vspace{3em}


:::: {layout="[0.3, 0.63, 0.07]"}
::: {#col-qrcode-repo-github}
\raggedright
```{r}
#| label: qrcode-repo-github
#| fig-align: right
#| echo: false

qr_code(
  "https://github.com/mvf-each-usp/estampa-camiseta-r-brasil",
  ecl = "L"
) |> 
  plot()
```
:::
::: {#col-texto}
\raggedleft
\fontsize{6}{8}\selectfont
\vspace{3em}
Feito com: RStudio, Quarto Markdown, \LaTeX\ e amor `S2`
\par
Fonte original:
\par
`https://github.com/mvf-each-usp/estampa-camiseta-r-brasil`
\par
Fonte atual:
\par
`https://github.com/o-seu-login/o-seu-repositorio`
\par
Entre e forke à vontade `=D`
:::
:::{#filler}
:::
::::
